|

### 2020-09-11 paper.Rmd
polishing discussion
removing notes

@@

Currently, the sage display is naive information in high dimensional space that is not captured by linear projections. Further work is required to investigate other transformations of the projections that can capture non-linear structure or that are locally linear, like the transformations performed by t-SNE.

* short summary of what you've done; introduced the sage display to 'reverse' the curse and applied it to several datasets in natural sciences and machine learning...

* pros of the proposed technique: alleviates overplotting issues,  better seperation of clusters and size of clusters; linear up to a point, point to pollen example; very quick to compute and still interpretable; point to examples here
How this would be applied in practice: clustering, classification?

* limitations of the proposed technique: finding appropriate parameters for data; acknowledge bunching but we are not able to capture what is happening - ignoring information in the high-d if you didn't rely on linear projections; possible introduces distortions point back that is also a problem for NLDR techniques but we see where it is happening

* further work or investigation: 
What other transformations on the projected data make sense?

Relationship with slice tour?
The recently introduced slice tour [@sliceTour] is essentially addressing the same issue, i.e. the overplotting of points from the large orthogonal space, but follows a different philosophy. Instead of mapping orthogonal volume to projected volume, we cut through the orthogonal space and only select a small portion of the volume for plotting. This is done by defining a slice via a cutoff on the orthogonal distance of points. The approach would be preferred in the case of large number of points, or for concave structure in the distribution, while the sage display works better in the case of limited sample size.

Relationship with nonlinear transformations such as tSNE?

>>>>

The recently introduced slice tour [@sliceTour] is essentially addressing the same issue, i.e. the overplotting of points from the large orthogonal space, but follows a different philosophy. Instead of mapping orthogonal volume to projected volume, we cut through the orthogonal space and only select a small portion of the volume for plotting. This is done by defining a slice via a cutoff on the orthogonal distance of points. The approach would be preferred in the case of large number of points, or for concave structure in the distribution, while the sage display works better in the case of limited sample size.

@@

Currently, the sage display is naive to information in high dimensional space that is not captured by linear projections. Further work is required to investigate other transformations of the projections that can capture non-linear structure or that are locally linear, like the transformations performed by t-SNE.
